---
title: "Assignment2"
author: "Bowen Zheng"
date: "9/9/2021"
output:
  word_document: default
  pdf_document: default
---

```{r}
library(rmarkdown)

```

(a) Fit a multiple regression model to predict Sales using Price, Urban, and US.
```{r}
library("ISLR")
?Carseats
data(Carseats)
fit <- lm(Sales ~ Price + Urban + US, data = Carseats)
summary(fit)
```



(b) Provide an interpretation of each coefficient in the model. Be careful—some of the variables in the model are qualitative!

1.When the price increases by $1000 and other forecasts remain unchanged, sales decrease by 54.459 units sold.

2.A store's sales are not affected by whether it is located in an urban area.

3.The sales volume of seats in US stores is 1200 higher than that in non-US stores

(c) Write out the model in equation form, being careful to handle the qualitative variables properly.

Sales=13.0434689+(−0.0544588)×Price+(1.2005727)×US+ε

US=1 is the store is in the US and 0 is not




(d) For which of the predictors can you reject the null hypothesis H0:βj=0H0:βj=0?

We can reject the null hypothesis for 'Urban' variables because p-value=0.936 > 0.05, it is not statistically significant.

(e) On the basis of your response to the previous question, fit a smaller model that only uses the predictors for which there is evidence of association with the outcome.

```{r}
fit2 <- lm(Sales ~ Price + US, data = Carseats)
summary(fit2)
```
(f) How well do the models in (a) and (e) fit the data?

 Neither model is good because R^2 is not high,only about 24% of the variability is explained by these 2 models.

(g) Using the model from (e), obtain 95% confidence intervals for the coefficient(s).

```{r}
confint(fit2)
```
(h) Is there evidence of outliers or high leverage observations in the model from (e)?

```{r}
par(mfrow = c(2, 2))
plot(fit2)
```